Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-20 newdraft.tex
Added a bunch
Added
-parahermitian section
-reworked para-calabi-yau
-mirror symmetry
-some refs

\subsubsection{Para-Complexified Version}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define following operations: para-complex conjugation $z=(x,y)\mapsto \bar{z}=(x,-y)$, i.e. $\overline{x+ky}=x-ky$, the real and imaginary parts given by $Re(z)=\frac{1}{2}(z+\bar{z})$, $Im(z)=k\frac{1}{2}(z-\bar{z})$, i.e. $Re(x+ky)=x,\ Im(x+ky)=y$.

@@

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}
\paragraph{The para-holomorphic volume form}
In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds. Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.

Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$. Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
\begin{Def}
Let $(\PS,K)$ be a para-complex manifold of dimension $2n$. We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
\begin{align*}
\pt \Omega=\p \tl{\Omega}=0.
\end{align*}
\end{Def}
Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.

As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
\begin{Def}
A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
\end{Def}

@@

\begin{Def}
A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
\begin{align}\label{eq:gen_nijenhuis}
\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
\end{align}
\end{Def}
Let $L_\KK$ and $\Tilde{L}_{\KK}$ denote the $+1$ and $-1$ eigenbundles of $\KK$, respectively. 
It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket. Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.

@@

\btd{Is there a classification of a most general GpC that can be written in the form
\[
\KK = 
\begin{pmatrix}
K & P \\
\omega & -K^*
\end{pmatrix}
\]
where $K \in {\rm End}(T)$, $P \in \wedge^2 T$ and $\omega \in \wedge^2 T^*$ satisfying some integrability conditions?
}

@@

The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
The fundamental observation is that the diagram
\[
\xymatrix{
& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
N & & X
}
\]
induces a pairing
\[
\begin{array}{ccccc}
 \Omega^p_N& \times & \Omega^q_X & \to & \Omega^{p+q-n}_{\cE(N, X)} \\
\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
 \end{array}
 \]
Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.

@@

The negative eigenbundle is $L_{\KK} = T^*$ with zero Lie algebroid structure.
The negative $2D$ theory is given by the AKSZ theory
\[
{\rm Map}(\Sigma_{dR} , T^*[1] M)
\]
where $T^*[1]M$ is equipped with its standard $1$-symplectic structure.

@@

We can also write the para-SUSY algebra in the more conventional off-diagonal basis $\{{Q}_\pm,\wtl{Q}_\pm\}$, in which the only non-zero brackets read:
\begin{align*}
[{Q}_\pm,\wtl{Q}_\pm]=-2\p_\pm.
\end{align*}
The two bases $\{Q^1_{\pm}, Q^2_\pm\}$ and $\{{Q}_\pm,\wtl{Q}_\pm\}$ are related by
\begin{align*}
Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm).
\end{align*}
Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
\begin{align*}
[Q_\pm,\overline{Q}_\pm]=2\p_\pm.
\end{align*}

@@

>>>>

\subsubsection{Para-Complexified Version}
In order to make the analogy between complex and para-complex geometry more explicit, one can \textit{paracomplexify} all objects by tensoring with the algebra $\mathbf{C}$ of \textbf{para-complex numbers}, which are given by ordered pairs $(x,y)\in \mathbb{R}\otimes (1,k)$ generated by $1$ and the symbol $k$, satisfying $k^2=1$ and called the para-complex unit. The elements $(x,y)\in \mathbf{C}$ can be therefore written as
\begin{align*}
\mathbf{C} \ni z=(x,y)=x+k\cdot y.
\end{align*}
On $\mathbf{C}$, we define the following familiar operations:\begin{align}
\begin{aligned}
&\bullet\quad \text{Para-complex conjugation: }x+\kk y\mapsto \overline{x+\kk y}=x-\kk y\\
&\bullet\quad \text{Real part: } x+\kk y \mapsto \text{Re}(x+\kk y)=x\\
&\bullet\quad \text{Imaginary part: } x+\kk y \mapsto \text{Im}(x+\kk y)=y.
\end{aligned}
\end{align}

@@

\newcommand{\Cp}{{\mathbf{C}}}
The isomorphism of para-complex vector spaces \eqref{para-complexification} induces an isomorphism between $\Lambda^{(p,q)}(T^*\PS)$ and $\Lambda^{p,q}(T^*\PS^\mathbf{C})$ as well as between the sections $\Omega^{(p,q)}$ and $\Omega_\Cp^{p,q}$, where the bigrading of the real bundle is with respect to the $\pm 1$ eigenvalues of $K$, while the bigrading of the para-complexified bundle is with respect to the $\pm k$ eigenvalues of $K$. Explicitly, we have
\begin{align}\label{isom_bigradings1}
\phi:\ (\ap,\tl{\ap})\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}\longmapsto \frac{1+k}{2}\ap + \frac{1-k}{2}\tl{\ap}\ \in\ \Omega_\Cp^{p,q}
\end{align}
with the inverse
\begin{align}
\phi^{-1}:\ \bm{\ap}\ \in\ \Omega_\Cp^{p,q}\longmapsto (\text{Re}(\bm{\alpha})+\text{Im}(\bm{\ap}),\text{Re}(\bm{\alpha})-\text{Im}(\bm{\ap}))\ \in\ \Omega^{(p,q)}\otimes \Omega^{(q,p)}.
\end{align}
The point we would like to emphasize here is that to one para-complex differential form of degree $p,q$ corresponds a {\it pair} of real forms in degrees $(p,q)$ and $(q,p)$. In particular, a para-complex form in degree $k,0$ corresponds to a pair of forms in degrees $(k,0)$ and $(0,k)$, i.e. a two $k$-forms on the two canonical para-complex foliations. Consequently, recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can easily deduce that the corresponding {\bf para-complexified Dolbeault complex} is given by
\begin{align}
\left( \Omega^{0,\bullet}_\Cp,\bar{\p}^\Cp\right),
\end{align}
In particular, the condition of holomorphicity in the para-complex coordinates $z^i\coloneqq \frac{1+k}{2}x^i+\frac{1-k}{2}\xt^i$ and $\bar{z}^i$ is equivalent to a local independence of the coordinates $\bar{z}^i$ and is therefore entirely analogous to complex geometry.
%\begin{lemma}
%Let $(\PS,K)$ be a paracomplex manifold. Then $\rd^p\coloneqq(\Lambda^{k+1}K)\circ\rd\circ (\Lambda^kK)$ can be expressed as
%\begin{align}\label{eq:dp-operator}
%\rd^p=\p_+-\p_-.
%\end{align}
%\end{lemma}
%\begin{proof}
%Let $\ap \in \Omega^{+m,-n}(\PS)$. Then we have
%\begin{align*}
%\rd^p\ap=(-1)^n(\Lambda^kK)\rd\ap=(-1)^{2n}\p_+ \ap +(-1)^{2n+1}\p_-\ap=(\p_+-\p_-)\ap,
%\end{align*}
%\end{proof}

%\paragraph{The para-holomorphic volume form}
%In K\"ahler geometry, the notion of a holomorphic volume form is very important and in particular gives rise to Calabi-Yau manifolds, perhaps the most important subclass of K\"ahler manifolds. Here we discuss the para-complex version of this story because it plays an important role when considering the anomalies of the R-symmetry at the quantum level.
%
%Remember that a holomorphic volume form on a complex manifold $M$ of complex dimension $k$ is a non-vanishing section of the canonical bundle, $\Omega \in \Omega^{(k,0)}(M)$, that is holomorphic, $\bar{\p}\Omega=0$. Recalling the para-complex Dolbeault complex \eqref{para-dolbeault}, we can immediately infer what should be the analogous object in para-complex geometry:
%\begin{Def}
%Let $(\PS,K)$ be a para-complex manifold of dimension $2n$. We define a {\bf para-holomorphic volume form} to be a nowhere vanishing section $\hat{\Omega}=(\Omega,\tl{\Omega})\in \Omega^{(n,0)+(0,n)}(\PS)$, where $\Omega \in \Omega^{(n,0)}(\PS)$ and $\tl{\Omega}\in \Omega^{(0,n)}(\PS)$ are each non-vanishing and satisfy
%\begin{align*}
%\pt \Omega=\p \tl{\Omega}=0.
%\end{align*}
%\end{Def}
%Because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, the above definition implies that $\Omega$ defines an honest volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and therefore both the canonical foliations $M$ and $\Mt$ of the para-complex manifold are orientable.
%
%As an extension of the above definition and the direct analogy with Calabi-Yau manifolds, we can introduce a definition of the para-Calabi-Yau manifolds:
%\begin{Def}
%A {\bf para-Calabi-Yau manifold} is a compact, para-K\"ahler manifold $(\PS,\eta,K)$ with a para-Holomorphic volume form $\hat{\Omega}$.
%\end{Def}

\subsubsection{Para-Hermitian Geometry}
We now introduce a metric $\eta$ compatible with the para-complex structure $K$, which by contraction $\eta \circ  K$ induces a non-degenerate two-form $\omega$. This gives rise to para-Hermitian geometry:
\begin{Def}
	Let $(\PS,K)$ be a para-complex manifold and let $\eta$ be a pseudo-Riemannian metric that satisfies $\eta(K\cdot,K\cdot)=-\eta$. Then we call $(\PS,K,\eta)$ a \textbf{para-Hermitian manifold}\footnote{If $K$ is not integrable, i.e. $(\PS,K)$ is almost para-complex, we would call $(\PS,K,\eta)$ an almost para-Hermitian manifold.}.
\end{Def}
\noindent
The above definition implies that the tensor $\omega\coloneqq \eta K$ is skew
\begin{align*}
\omega(X,Y)=\eta(KX,Y)=-\eta(X,KY)=-\omega(Y,X),
\end{align*}
and nondegenrate (because $\eta$ is nondegenerate), therefore $\omega$ is an almost symplectic form, sometimes called the \textbf{fundamental form}. From $K^2=\id$ we also have $K=\eta^{-1}\omega=\omega^{-1}\eta$. Another observation is that since the eigenbundles of $K$ have the same rank, $\eta$ has split signature $(d,d)$. Furthermore, the eigenbundles of $K$ are isotropic with respect to both $\eta$ and $\omega$. This means that the almost symplectic form $\omega$ is of the type $(1,1)$, $\omega \in \Omega^{(1,1)}(\PS)$.
\begin{remark}
	As shown above, the data $(\PS,K,\eta)$, $(\PS,\eta,\omega)$ and $(\PS,K,\omega)$ are on a para-Hermitian manifold equivalent and so we may use the different triples interchangeably to refer to a para-Hermitian manifold.
\end{remark}
Again, in a complete analogy with K\"ahler geometry, we get para-K\"ahler geometry whenever the fundamental form $\omega$ is closed
\begin{Def}
	Let $(\PS,\eta,\omega)$ be a para-Hermitian manifold with $\rd\omega=0$. We call $(\PS,\eta,\omega)$ a \textbf{para-K\"ahler manifold}.
\end{Def}

\paragraph{Para-Calabi-Yau geometry}

In \cite{mythesis}, the notion of para-Calabi-Yau geometry is introduced. As the name suggests, these manifolds should play the role of the para-complex version of Calabi-Yau manifolds in complex geometry. We now recall some basic properties of para-Calabi-Yau manifolds, motivating the definition by Calabi-Yau geometry, which is a standard notion in the literature.

There are many different ways to define what a Calabi-Yau manifold is, but for the purpose of our discussion we will call a Calabi-Yau manifold a K\"ahler manifold $(M,g,I)$ with the holonomy group of the underlying Riemannian metric to be $\text{Hol}(g)\subseteq SU(d)$, as opposed to $U(d)$, which is the case for ordinary K\"ahler manifolds.\footnote{Typically, a part of the definition of a Calabi-Yau manifold is the requirement of compactness of $M$ and sometimes, one requires that $\text{Hol}(g)$ is exactly equal to $SU(d)$.} A consequence of this property is that there exists a {\it holomorphic volume form}, i.e. a non-vanishing section $\Omega \in \Omega^{d,0}$ that is holomorphic, $\bar{\p}\Omega=0$ and satisfies
\begin{align*}
    \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2}\left(\frac{i}{2}\right)^d \Omega\w \bar{\Omega},
\end{align*}
where $\omega=gI$ is the K\"ahler form.

% a Calabi-Yau manifolds

% A Calabi-Yau manifold is a K\"ahler manifold $(M,\omega,I)$ of complex dimension $k$ with a non-vanishing holomorphic volume form $\Omega$,
% \begin{align*}
%     \Omega \in \Omega^{(k,0)}(M),\quad \bar{\p}\Omega=0,
% \end{align*}
% which satisfies a compatibility condition with the K\"ahler fundamental form $\omega$ (sometimes called the complex Monge-Ampere equation)
% \begin{align*}
%     \frac{\omega^k}{k!}=(-1)^\frac{k(k-1)}{2}\left(\frac{i}{2}\right)^k \Omega\w \bar{\Omega}.
% \end{align*}
% Calabi-Yau manifolds play an important role in theoretical physics, especially in string theory where they serve as the geometric model for string compactifications. For more details on Calabi-Yau manifolds, the reader may consult for example the book \cite{joyce2000compact}.

We now turn to the analogue of the above notions in the para-complex setting. Let $(K,\eta,\omega)$ be a $2d$-dimensional para-K\"ahler manifold with $\lc$ the Levi-Civita conencion of $\eta$. From $\lc\omega=\lc\eta$, we have that the holonomy group of a para-K\"ahler manifold is $GL(d)=O(d,d)\cap Sp(2d)$. For a para-Calabi-Yau manifold, the natural definition is therefore the following:

\begin{Def}
A {\bf para-Calabi-Yau manifold} is a para-K\"ahler manifold $(\PS,K,\eta)$ of dimension $2d$ such that the holonomy group of $\eta$ is $\text{Hol}(\eta)\subseteq SL(d)$.
\end{Def}
\begin{remark}
Note the interesting property that both $SU(d)$ and $SL(d)$ are real forms of $SL_\mathbb{C}(d)$.
\end{remark}

Let us now investigate what is the structure on para-Calabi-Yau analogous to the holomorphic volume form. We choose the local adapted coordinates $(x^i,\xt_j)$ in which $\eta$ and $\omega$ have the canonical form
\begin{align*}
    \eta=dx^i\otimes d\xt_i+d\xt_i\otimes dx^i,\quad \omega=dx^i\w d\xt_i.
\end{align*}
Because the holonomy of $\eta$ is now contained in $SL(d)$, there is also a covariantly constant tensor $\hat{\Omega}$
\begin{align*}
    \hat{\Omega}=dx^1\w\cdots\w dx^d+d\xt_1\w\cdots\w d\xt_d=\Omega+\tl{\Omega},
\end{align*}
which satisfies $\pt\Omega=\p\tl{\Omega}=0$ as well as
\begin{align*}
   \frac{\omega^d}{d!}=(-1)^\frac{d(d-1)}{2} \Omega\w \tl{\Omega}. 
\end{align*}

We call $\hat{\Omega}=(\Omega,\tl{\Omega})$ a {\bf para-holomorphic volume form}. Remember that on a para-complex manifold $\PS$ of dimension $2n$, the appropriate analogue of the holomorphic forms are the para-holomorphic forms, given by pairs $(\alpha,\tl{\alpha})\in\Omega^{(k,0)+(0,k)}(\PS)$ (here the bigrading is with respect to the para-complex structure), satisfying $\pt\ap=\p\tl{\ap}=0$. Therefore, the {para-holomorphic volume form} is exactly the correct analogue of the holomorphic volume form in case of the Calabi-Yau manifolds. Furthermore, because $\Omega^{(n,0)}(\PS)$ is naturally isomorphic to $\Omega^n(M)$, the section $\Omega$ is non-vanishing and $\pt \Omega=0$ implies it is invariant under the translation along $\Mt$, and so it defines a volume form on $M$. Similarly, $\tl{\Omega}$ is a volume form on $\Mt$ and we see that the para-Calabi-Yau structure on $\PS$ augments the canonical foliations $M$ and $\Mt$ of the para-complex manifold with volume forms and both the foliation manifolds are consequently orientable.

@@

\begin{Def}
A \textbf{(twisted) generalized para-complex} (GpC) structure $\KK$ is an endomorphism of $\TT$, such that $\KK^2=\id$ and $\la\KK,\KK\ra=-\lara$, whose generalized Nijenhuis tensor vanishes:
\begin{align}\label{eq:gen_nijenhuis}
\mathcal{N}_\KK(u,v)=[\KK u,\KK v]_H+\KK^2[ u,v]_H-\KK([\KK u,v]_H+[ u,\KK v]_H)=0.
\end{align}
\end{Def}

It is a straightforward exercise to check that the most general form of an almost GpC structure is given by
\begin{align}\label{eq:GpC_generalform}
 \KK =
 \begin{pmatrix}
 A & \Pi \\
 \Omega & -A^*
 \end{pmatrix}, \text{ with }
 \begin{cases}
  A^2 + \Pi \Omega & = \id\\
  A\Pi - \Pi A^* & = 0\\
  \Omega A + A^*\Omega & = 0
 \end{cases}.
\end{align}
where $A \in \End(T)$ and $\Omega \in \Omega^2(M)$, $\Pi \in \se(\Lambda^2 T)$ are skew tensors. The integrability conditions on these tensors are a bit more involved and we will only discuss their special cases when discussing examples. An interested reader can consult \cite{crainic-integrability}, where the integrability is presented in the most general form for generalized complex structures, where the conditions are analogous.

Let $L_\KK$ and $\Tilde{L}_{\KK}$ denote the $+1$ and $-1$ eigenbundles of $\KK$, respectively. 
It is easy to check that the condition \eqref{eq:gen_nijenhuis} is equivalent to the $\pm 1$ eigenbundles of $\KK$ to be involutive under the twisted Dorfman bracket. Since in this paper the flux $H$ will be generically non-zero but all results hold for the special case $H=0$ as well, we will drop the word ``twisted" from our definitions.

@@

@@

The AKSZ construction endows the mapping space $\cE(N, X)$ in (\ref{eqn: map}) with a $(-1)$-shifted symplectic symplectic form as follows, compatible with the homological vector field $\d_{\cN} + Q$ as follows.
The fundamental observation is that the diagram
%\[
%\xymatrix{
%& N \times \cE(N, X) \ar[dr]^-{{\rm ev}} \ar[dl]_-{\pi_N} & \\
%N & & X
%}
%\]
\begin{equation*}
	\begin{tikzcd}
	& N \times \cE(N, X)\arrow{rd}{{\rm ev}}\arrow[swap]{ld}{\pi_N} &\\
	N & & X
	\end{tikzcd}
\end{equation*}
induces a pairing
\[
\begin{array}{ccccc}
 \Omega^p_N& \times & \Omega^q_X & \to & \Omega^{p+q-n}_{\cE(N, X)} \\
\displaystyle \alpha & \times & \beta & \mapsto & \displaystyle \int_N \pi_N^* \alpha \wedge {\rm ev}^* \beta 
 \end{array}
 \]
Applied to the element $1 \times \omega_X \in \Omega^0_N \times \Omega^{2}_X$ we obtain a $(-1)$-shifted symplectic form that we denote $\int_N \omega_X$.

@@

The negative eigenbundle is $L_{\KK} = T^*$ with zero Lie algebroid structure.
The negative $2D$ theory is given by the AKSZ theory
\[
{\rm Map}(\Sigma_{dR} , T^*[1] M)
\]
where $T^*[1]M$ is equipped with its standard $1$-symplectic structure. \david{so is this the BFF theory?}

@@

We can also write the para-SUSY algebra in the more conventional off-diagonal basis $\{{Q}_\pm,\wtl{Q}_\pm\}$, in which the only non-zero brackets read:
\begin{align*}
[{Q}_\pm,\wtl{Q}_\pm]=-2\p_\pm.
\end{align*}
The two bases $\{Q^1_{\pm}, Q^2_\pm\}$ and $\{{Q}_\pm,\wtl{Q}_\pm\}$ are related by
\begin{align}\label{parasusy_offdiagonal_basis}
Q_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm-Q^1_\pm),\quad \wtl{Q}_\pm=\frac{1}{\sqrt{2}}(Q^2_\pm+Q^1_\pm).
\end{align}
Again, this is analogous to the complex basis of the ordinary $(2,2)$ superalgebra
\begin{align}\label{complex_(2,2)}
[Q_\pm,\overline{Q}_\pm]=2i\p_\pm.
\end{align}

@@

\section{Para-complex semi-flat mirror symmetry}
In this section we present our first observations about a possible notion of mirror symmetry for para-complex geometry. We show that the initial observations about $2D$ $(2,2)$ SUSY $\sigma$-models that initiated the vast research program of mirror symmetry apply perfectly well to $(2,2)$ para-SUSY models and therefore give rise to parallel statements in the para-holomorphic category.

The original example of mirror symmetry in physics is based on the observation that the $(2,2)$ SUSY algebra (in its complex form) exhibits a $\mathbb{Z}_2$ outer endomorphism, which exchanges the vector and axial $U(1)$ generators and in particular then exchanges the two topological twists \cite{Witten_mirror_topological}. On the level of the supercharges \eqref{complex_(2,2)}, this is manifested by the exchange (see for example \cite{susy_hori} for details)
\begin{align*}
Q_-\longleftrightarrow \overline{Q}_-,
\end{align*}
which clearly preserves the commutation relations. In our case, the $\mathbb{Z}_2$ symmetry acts on \eqref{parasusy_offdiagonal_basis} as
\begin{align*}
Q_-\longleftrightarrow \widetilde{Q}_-,
\end{align*}
or, equvalently on the diagonal basis \eqref{eq:(2,2)para} $Q^2_-\mapsto -Q^2_-$, as discussed in Section \ref{sec:toptwist}, where we also argued that this exchanges the two types of topological twists.

The geometric realization of the above-described $\mathbb{Z}_2$ action on the $(2,2)$ superalgebra was described in \cite{SYZ} and since has acquired the name SYZ mirror symmetry. There, the mirror symmetry is described as a correspondence between pairs of Calabi-Yau manifolds $M$ and $\Mt$, specifically ones that admit a particular types of fibrations over the same base $B$. The mirror symmetry in this case acts geometrically as an exchange of these fibrations, which are essentially linear duals to each other. One of the hallmarks of mirror symmetry is the feature that it relates the moduli space of symplectic structures on $M$ with a moduli space of complex structures on $\Mt$. On the physics side, this exchange is realized as a correspondence between an $A$-model on $M$ and a $B$-model on $\Mt$.

In the following paragraphs, we will study the semi-flat case of SYZ mirror symmetry, where the pair of K\"ahler Calabi-Yau manifolds is given by $M=TB$ and $\Mt=T^*B$, the tangent and cotangent bundles of an affine manifold $B$. Our result is that this setting admits an equally natural description in terms of para-K\"ahler and para-Calabi-Yau geometry, where the mirror map exchanges the {\bf symplectic moduli} on $M$ with the {\bf para-complex moduli} on $\Mt$. The underlying symplectic fundamental forms of both the K\"ahler and para-K\"ahler gometries coincide, while the complex and para-complex structures anti-commute and therefore the triple $(\omega,K,I)$ defines {\it Born geometry} \cite{freidel2014born,Freidel:2018tkj,mythesis} (see also \cite{Marotta:2018myj,Hassler:2019wvn,Marotta:2018swj,Marotta:2019eqc}). Consequently, the mirror map in the semi-flat case relates Born geometries on $M$ and $\Mt$, mapping between the symplectic moduli on one side and the para-complex and complex moduli on the other side.

In the following we closely follow the discussions presented in \cite{mythesis,mirror_w-o_corrections,hitchin1997moduli}

\paragraph{The para-complex point of view} We start with the discussion of the para-Calabi-Yau geometry on the side of $M$ and then contrast it with the Calabi-Yau geometry of $M$. Consider an affine manifold $B$ and take a neighbourhood $U\subset B$ with local coordinates $u^i$. Let $U\times \RR^n$ with the coordinates $(u^i,v^i)$, $v^i$ denoting the coordinates on $\RR^n$, be the local model for $M=TB$. We define the para-complex structure on $M$ in terms of its adapted coordinates $(x^i=u^i+v^i,\xt_j=u^k-v^k)$. The fact that $M$ is affine means that the transition functions are in $GL_n(\RR)\ltimes \RR^n$, i.e. of the form
\begin{align*}
    u^i\mapsto u'^i(u^i)=A_{\ j}^{i}u^j+B^i,\quad A \in GL_n,\ B\in \RR^n.
\end{align*}
This implies that the natural fiber coordinates of $TM$, $v^i=du^i$,  transform as $u^i\mapsto A^i_{\ j}u^j$, so that the combinations $(x^i=u^i+v^i,\xt^j=u^k-v^k)$ transform by
\begin{align*}
    (x^i,\xt_j)\mapsto (A_{\ k}^{i}x^k+B^i,A_{\ k}^{j}\xt^k+B^j),
\end{align*}
which assures that the total space of $TB$ is an affine manifold with $(x^i,\xt^j)$ affine coordinates. In particular $(x^i,\xt^j)$ are adapted coordinates of an integrable para-complex structure on $TB$, because the transition functions are para-holomorphic.

We now endow $M$ with a para-Calabi-Yau structure defined by the fundamental form $\omega$ and a para-Holomorphic volume form $\Omega$:
\begin{align*}
    \omega&=\omega_{ij}\ dx^i\w d \xt^j=2\omega_{ij}\ du^i\w dv^j,\\
    \hat{\Omega} &=dx^1\w\cdots\w dx^n+d\xt^1\w\cdots\w d\xt^n=\Omega+\tl{\Omega}.
\end{align*}
We also assume that the local para-K\"ahler potential $\phi$ on $U\subset M$, which defines $\omega$ via
\begin{align*}
\omega_{ij}=\p_i\pt^j\phi=\left(\frac{\p^2}{\p u^i \p u^j}-\frac{\p^2}{\p v^i \p v^j}\right)\phi,
\end{align*}
is of the form $\phi(u,v)=\phi(u)$. This means it is invariant under the translations in the fiber directions of $TB$ and the geometry is therefore {\it semi-flat}, hence the name semi-flat mirror symmetry. The fact that the pair $(\omega,\hat{\Omega})$ defines a para-Calabi-Yau structure means that it satisfies the Monge-Ampere equation:
\begin{align*}
    C\omega^n=\Omega\w\tl{\Omega} \Longleftrightarrow   \text{det}(\frac{\p^2\phi}{\p u^i\p u^j})=C.
\end{align*}
The above has a unique solution for $\phi$ \cite{calabi1975construction} assuming $\phi\mid_{\p U}=0$ and $\phi$ is convex ($\p_i\p_j\phi>0$). For the Monge-Ampere equation to be invariant under the affine transformations, we must have $\text{det}(A)=1$, which is a requirement that defines a {\it special affine manifold}. Therefore, we will from now on require that $B$ is special affine. For completeness, we note that the para-K\"ahler metric $\eta$ takes the form
\begin{align*}
    \eta=\omega_{ij} (dx^i\otimes d\xt^j+d\xt^i\otimes dx^j)=2\omega_{ij}(du^i\otimes du^j-dv^i\otimes dv^j).
\end{align*}

\paragraph{The complex point of view}
In the usual discussion of the semi-flat mirror symmetry, one considers a complex structure defined by the holomorphic coordinates $z^i=u^i+iv^i$ instead of the para-complex structure above. The fundamental form is then taken to be $\omega_I=i\p\bar{\p}\phi$, which in the semi-flat case $\phi(u,v)=\phi(u)$ coincides with $\omega$. The Riemannian K\"ahler metric is then
\begin{align*}
    g=\omega_{ij}(du^i\otimes du^j+dv^i\otimes dv^j).
\end{align*}
It is easy to show that $I$ and $K$ anticommute, and because $\omega_I=\omega$, we see that this geometric setting defines Born geometry.
\newcommand{\uh}{\hat{u}}
\newcommand{\vh}{\hat{v}}
\newcommand{\xh}{\hat{x}}
\newcommand{\xth}{\hat{\xt}}
